---
title: "p8105_hw5_at3346"
author: "Ashley Tseng"
date: "11/3/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(broom)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Problem 1
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  janitor::clean_names() %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(species = as.character(species))


iris_func = function(x) { 
  
  if (is.numeric(x)){
      replace(x, is.na(x), round(mean(x, na.rm = TRUE), digits = 1))
  }
  
  else {
    replace (x, is.na(x), "virginica")
  }
  
}
  
iris_no_missing = map_df(iris_with_missing, ~iris_func(.x))
```



## Problem 2
```{r}
file_names = tibble(
  name = list.files(path = "./data/", all.files = TRUE, no.. = TRUE),
  file_path = str_c("./data/", name))

source_func = function(x){
  read_csv(x)
}

long_study = file_names %>% 
  mutate(source_name = map(file_names$file_path, source_func)) %>% 
  unnest() %>% 
  janitor::clean_names() %>% 
  select(-file_path) %>% 
  separate(name, into = c("study_arm","subject_id", "file_type")) %>%
  select(-file_type)
```


```{r spaghetti_plot}
spaghetti = long_study %>% 
    pivot_longer(
    cols = starts_with("week_"),
    names_to = "week",
    names_prefix = "week_",
    values_to = "obs_value") %>% 
  group_by(subject_id) %>% 
  ggplot(aes(x = week, y = obs_value, color = study_arm, group = study_arm)) + 
  geom_path() +
  labs(
    title = "Observations On Each Subject Over Time",
    x = "Week",
    y = "Weekly Observation Value",
    color = "Study Arm") +
  theme(plot.title = element_text(hjust = 0.5))

spaghetti
```


***ADD MORE***
Based on visually inspecting the spaghetti plot, the weekly observation values for subjects in the experimental arm of the study are, on average, greater than the weekly observation values for the control arm of the study. 



## Problem 3

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of β2 on the x axis. Describe the association between effect size and power.
```{r}
set.seed(10)

sim_regression = function(n = 30, beta0 = 2, beta1, var = 50) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, var)
  )

  ls_fit = lm(y ~ x, data = sim_data)
  
  tidy(ls_fit)
}


sim_results = 
  rerun(10000, sim_regression(n = 30, beta0 = 2, var = 50, beta1 = 0)) %>% 
  bind_rows() %>% 
  select(term, estimate, p.value) %>% 
  filter(term == "x")


sim_results_power = 
  tibble(beta1_values = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_lists = map(.x = beta1_values, ~rerun(10000, sim_regression(beta1 = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs) %>% 
  select(beta1_values, term, estimate, p.value) %>% 
  filter(term == "x") 


sim_results_all =
  sim_results_power %>% 
  group_by(beta1_values) %>% 
  summarize(
    p_sum = sum(p.value < 0.05),
    p_total = p_sum/n()) %>% 
  ggplot(aes(x = beta1_values, y = p_total)) + 
  geom_bar(stat = "identity", fill = "sea green") +
  labs(
    title = "Association Between Effect Size & Power",
    x = "True Value of Beta1 (Effect Size)",
    y = "Proportion of Times The Null Was Rejected (Power)") +
  theme(plot.title = element_text(hjust = 0.5))

sim_results_all
```

